A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
added more conclusions on classification.

Analyzing the models produced, one can see that having a high capital gain 
clearly contributes to gaining more than 50K dollars per year. On the other
hand, part time workers usually don't gain more than 50K dollars per year, like
the younger and not married people.

>>>>

Analyzing the models produced, one can see that having a high capital gain 
clearly contributes to gaining more than 50K dollars per year. On the other
hand, part time workers usually don't gain more than 50K dollars per year, like
the younger and not married people. Having a higher education clearly 
contributes to gaining more money, as does a stable life (married people
gain more). People who work in private businesses or in the government are also
more suitable to gain above 50K dollars per year. Working more hours per week
obviously contributes to getting more money. Some less obvious conclusions show 
that being a black own child, even though working more than 40 hours per week 
doesn't lead to winning more than 50K dollars per year. In fact, being an own 
child appears on a lot of rules describing people who win less than 50K. ILP
also builds some interesting clauses where the nationality is associated with.
This shows that being a native of some asian countries, such as taiwan, thailand
or cambodia usually lead to gaining more than 50K dollars per year.

Classification is a very active area on the machine learning research field, as
the great amount of software tools and algorithms to tackle it show. It has
arrived to a state where efficient models are built fast and with an expression
suitable for analysis by a human agent. Progresses in relational data mining are
allowing models to infer relations between entities, expanding their range of 
applications by a lot. This work enabled a broad study of different types of 
classification algorithms, analyzed both in terms of efficiency and 
expressiveness of the models produced. Taking that into account, classification
is nowadays a very reliable process for data analysis at large.
